Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-03-24 MUSES_vs_BYOD_solutions.tex

\section{Acknowledgements}
This paper has been funded in part by European project MUSES (FP7-318508), along with Spanish National project TIN2011-28627-C04-02 (ANYSELF), and GENIL PYR-2014-17, awarded by the CEI-BioTIC UGR.

@@

\end{document}

>>>>

\section{Acknowledgements}
This paper has been funded in part by European project MUSES
(FP7-318508), along with Spanish National projects
TIN2011-28627-C04-02
(ANYSELF) and TIN2014-56494-C4-3-P (EphemeCH), and GENIL PYR-2014-17,
awarded by the CEI-BioTIC UGR.

@@

\bibliography{geneura-latin1,review_muses}

\end{document}
%%% Local Variables:
%%% ispell-local-dictionary: "english"
%%% hunspell-local-dictionary: "english"
%%% End:
